{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-03 Paper/main.tex
Functional data set

@@

	\subsection{Functional Data Sets}

	Consider the case of a data set containing observations $X_i(t)$ of a random function $X(\omega)(t)$, measured at discrete points $t_{j,i}$:

	\begin{equation}
		x_{i}(t_{j,i}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{j,i} \in [T_1, T_2]
	\end{equation}

 	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points. Therefore, this can be seen as set of discretized approximations of the realizations of a random function.
	As in the finite dimensional setting, the concept of identically distributed and independent data is important. This concept generalizes to the case of functional data using the concepts for general random variables.

	An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples. Together with a set of responses, this then can be used to perform functional linear regression, as will be subject of the simulation and application.

>>>>

	\subsection{Functional Data Set}
	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$:

	\begin{equation}
		x_{i}(t_{i,j}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{i,j} \in [T_1, T_2]
	\end{equation}

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points. As it can be seen, the measurmant points can be differentiated through each sample. However, this is not a primary interest of this paper, and, therefore, we consider the case where every measurement point exists evenly, namely, that $t_{i,j}$ and $J_i$ are identical for all $i$. In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable. The several basis systems to make the functional data smooth is introduced from the next sub-chapter.\\
	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis. The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible. An example of such a data set could be the data set of 60 N

@@

	\subsection{Functional Data Sets}
	{\color{orange} Move this part below 3.2?}
	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$:

	\begin{equation}
		x_{i}(t_{i,j}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{i,j} \in [T_1, T_2]
	\end{equation}

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points. As it can be seen, the measurmant points can be differentiated through each sample. However, this is not a primary interest of this paper, and, therefore, we consider the case where every measurement point exists evenly, namely, that $t_{i,j}$ and $J_i$ are identical for all $i$. In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable. The several basis systems to make the functional data smooth is introduced from the next sub-chapter.\\
	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis. The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible. An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples in which each spectra was randomly selected and evenly measured.
